Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
to include
fix mayor

<!-- spatial -->
Habitat selection, the use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Social structure and 
habitat selection are intimately related and individuals must
share space to interact [@Webber_2018]. Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, the (3) habitat patches within the home range and
(4) specific resources within a habitat patch. Kie et al. [-@Kie_2002] found
that, independently, third order of selection was insufficient for capturing
landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
scale larger than their home range size. Scales of habitat selection could be 
relevant for multilayer networks and our integration of habitat within a 
multilayer context could be an important first step (see Figure \@ref(fig:lcres)). 
Specifically, if individuals select habitats at the 
home range scale, it may be relevant to assess social structure at 
the home range overlap scale in a multilayer framework. By contrast,
in cases where individuals select habitats at the patch-scale, 
more fine-scale measures of sociality may be relevant. Moving past this hierarchical
perspective, Mayor (2007) emphasized the importance of considering a broad
continuum of scales to reveal scale-dependent selection and avoid the bias of
predefined scales assumed to be associated with certain behaviours.

@@

<!-- temp -->
The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information. 
<!-- TODO: results -->

@@

<!-- temp --> 
Changes in network metrics through time can explain the influence
of seasonality of resources on animal sociality. Using an ordinal multilayer
network composed of 20 discrete time windows throughout the study period, we
observed periods of increased sociality in caribou on Fogo Island. Edge overlap
was higher during fall, winter and spring (approximately October - June) than in
summer (approximately June - October)  (Figure \@ref(fig:temp) A). Similarly,
individual graph strength was also higher in these periods (Figure
\@ref(fig:temp) C). These periods of increased sociality correspond to seasons of
heterogeneous resource availability [Peigner_2019]. By explicitly considering
the temporal context of social interactions in separate layers, multilayer
networks provide a detailed and dynamic perspective of animal social networks.
In addition, this could be extended using time-aggregated networks and a
moving-window approach to inform the temporal scale including time window size
and sampling effort [@Farine_2017; @Bonnell_2020]. 
<!-- temp -->

>>>>

<!-- spatial -->
Habitat selection, the use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Social structure and 
habitat selection are intimately related and individuals must
share space to interact [@Webber_2018]. Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, the (3) habitat patches within the home range and
(4) specific resources within a habitat patch. Kie et al. [-@Kie_2002] found
that, independently, third order of selection was insufficient for capturing
landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
scale larger than their home range size. Scales of habitat selection could be 
relevant for multilayer networks and our integration of habitat within a 
multilayer context could be an important first step (see Figure \@ref(fig:lcres)). 
Specifically, if individuals select habitats at the 
home range scale, it may be relevant to assess social structure at 
the home range overlap scale in a multilayer framework. By contrast,
in cases where individuals select habitats at the patch-scale, 
more fine-scale measures of sociality may be relevant. Moving past this hierarchical
perspective, Mayor et al. [-@Mayor_2007] emphasized the importance of considering a broad
continuum of scales to reveal scale-dependent selection and avoid the bias of
predefined scales assumed to be associated with certain behaviours.

@@

<!-- temp -->
The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information. 
<!-- TODO: results

Edge overlap
was higher during fall, winter and spring (approximately October - June) than in
summer (approximately June - October)  (Figure \@ref(fig:temp) A). Similarly,
individual graph strength was also higher in these periods (Figure
\@ref(fig:temp) C). These periods of increased sociality correspond to seasons of
heterogeneous resource availability [Peigner_2019].

By explicitly considering
the temporal context of social interactions in separate layers, multilayer
networks provide a detailed and dynamic perspective of animal social networks.
In addition, this could be extended using time-aggregated networks and a
moving-window approach to inform the temporal scale including time window size
and sampling effort [@Farine_2017; @Bonnell_2020]. 
-->

@@
